### 2022-11-29 paper.Rmd
minor

To optimize overall between-group similarity---and hence to overcome the limitations of k-means anticlustering---this paper introduces k-plus anticlustering. K-plus is an extension of the k-means objective that includes one or several terms to quantify between-group similarity with regard to other distribution characteristics instead of only the mean. Specifically, k-plus offers the possibility to minimize differences with regard to the variance, covariances, and higher order moments such as skewness and kurtosis. The k-plus criterion is not a single criterion for anticlustering, but a familiy of objectives implementing different requirements with regard to between-group similarity. After formally introducing the k-plus objective, a simulation study is reported showing that k-plus anticlustering is well suited to create groups having minimal differences according to multiple distribution characteristics. Two pratical are included that illustrate how readers can easily apply k-plus anticlustering using the free and open source software package `anticlust`, an extension to the popular statistical programming language R [@papenberg2020; @R-base; @R-anticlust].

@@

Generally, it should be noted that diversity anticlustering is a good all-arounder method that tends to somewhat addressed all distribution characteristics. For the specific objectives that are addressed by the k-plus methods, however, diversity anticlustering was outperformed. As as side note, apart from k-plus correlation, diversity anticlustering was the only method that equalizes correlation structure among groups. As far as I know, this observation has not been made previously, even though the maximum diversity problem has been widely studied.

@@

Table 3 illustrates another advantage of k-plus anticlustering over diversity anticlustering: When creating groups of unequal size, diversity anticlustering tends to increase the spread of the data in the largest group in comparison to the other groups. This is due the diversity criterion being a measure of within-group heterogeneity; maximizing within-group heterogeneity only incidentally maximizes between-group similarity. Because the diversity criterion is a sum rather than an average, the correspondence between within-group heterogeneity and between-group similarity does not hold for unequal-sized groups. K-plus anticlustering strives for between-group similarity regardless of group size.

>>>>

To optimize overall between-group similarity---and hence to overcome the limitations of k-means anticlustering---this paper introduces k-plus anticlustering. K-plus is an extension of the k-means objective that includes one or several terms to quantify between-group similarity with regard to other distribution characteristics instead of only the mean. Specifically, k-plus offers the possibility to minimize differences with regard to the variance, covariances, and higher order moments such as skewness and kurtosis. The k-plus criterion is not a single criterion for anticlustering, but a familiy of objectives implementing different requirements with regard to between-group similarity. After formally introducing the k-plus objective, a simulation study is reported showing that k-plus anticlustering is well suited to create groups having minimal differences according to multiple distribution characteristics. Two practical examples are included that illustrate how readers can easily apply k-plus anticlustering using the free and open source software package `anticlust`, an extension to the popular statistical programming language R [@papenberg2020; @R-base; @R-anticlust].

@@

Generally, it should be noted that diversity anticlustering is a good all-arounder method that tends to somewhat addressed all distribution characteristics. For the specific objectives that are addressed by the k-plus methods, however, diversity anticlustering was outperformed. As as side note, apart from k-plus correlation, diversity anticlustering was the only method that equalizes correlation structure among groups. To the best of my knowledge, this observation has not been made previously, even though the maximum diversity problem has been widely studied.

@@

Table 3 illustrates another advantage of k-plus anticlustering over diversity anticlustering: When creating groups of unequal size, diversity anticlustering tends to increase the spread of the data in the largest group in comparison to the other groups. This is due the diversity criterion being a measure of within-group heterogeneity. Because the diversity criterion is a sum rather than an average, the correspondence between within-group heterogeneity and between-group similarity does not hold for unequal-sized groups. K-plus anticlustering strives for between-group similarity regardless of group size.
